---
project:
  title: "Daily-assignments"
  output-dir: docs

format:
  html:
    self-contained: true
execute: 
  echo: true
---
```{r}
install.packages("dplyr")
library(dplyr)
install.packages("visdat")
library(visdat)
library(tidyr)
install.packages("broom")
install.packages("tidyverse")
library(tidyverse)
library(ggplot2)
```

```{r}
?airquality
vis_dat(airquality)
```
# Yes, these data need cleaning. 

```{r}
cleaned_airdata <- airquality %>% drop_na(Ozone) %>% drop_na(Solar.R)
vis_dat(cleaned_airdata)
summary(cleaned_airdata)
```
# Now that the data are cleaned, I'm choosing to use temperature as the predictor variable because ozone and temperature have a strong correlation. Ozone formation is highly impacted by temperature, often showing a positive correlation. 

```{r}
model <- lm(Ozone ~ Temp, data = cleaned_airdata)
summary(model)
```
# After using the summary function, I think this is a valid model since the R^2 value is much greater than zero and the residual standard error is a low value. Further, the significance code shows these two variables are highly significant. 

# The R squared value of 0.4833 means that the temperature explains about 50% of the ozone levels variation. This means temperature has decently good predictive ability for predicting ozone levels, but these levels are also influenced by other factors.

```{r}
a_data <- broom::augment(model, cleaned_airdata)
head(a_data)
```
```{r}
ggplot(a_data, aes(x = .fitted, y = Ozone)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red") + 
  labs(title = "Actual VS Predicted Ozone Levels",
        subtitle = paste("Correlation:", round(cor(a_data$Ozone, 
                                                   a_data$.fitted),2)), 
        x = "Predicted Ozone Levels", 
        y = "Actual Ozone Levels") +
  theme_minimal() 
```
# This graph shows the linear relationship between predicted and actual Ozone levels, highlighting a strong correlation of 0.7. 
